Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact

### 2019-07-10 tse19/main.tex
updates table

It is important to note that we under-estimated running times as we missed test modules not enabled for
execution in the root \emph{pom.xml}.\Comment{Some projects may omit long-running tests on their default
execution.}  \textcolor{red}{[S.J: existe a possibilidade de criar uma script que identifica no pom.xml raiz, quais projetos tem testes habilitados por custom params? @Marcelo @Marcio voces acham interessante colocar esses dados aqui ? quantos projetos possuem essa caracteristica.  ]}For instance, the project \CodeIn{springboot-security-jwt}
runs all unit tests in a few seconds.  According to our criteria, this
project is classified as \shortg{} but a closer look reveals
that only smoke tests are executed in this project by default.
In this project, integration and system tests, which take longer to run, are only accessible via
custom parameters, which we do not handle in our experimental setup.
We enabled such parameters for this specific project and observed that
testing time goes to nearly 30 minutes.  For simplicity, we considered
only the tests executed by default.
From the \numSubjs{} testable projects, \numSubjsPass{} successfully
executed all tests and \numSubjsFail{} reported some test failure.
From these \numSubjsFail{} subjects, only 9 subjects
have more than 5\% of failing tests (5.1\% on average).
\begin{mdframed}
\noindent\textit{Answering \numRQFeasibilityOne{}:}~\emph{We conclude that
    time-consuming test suites are relatively frequent in
    open-source projects.  We found that \percentMedRunning{} of
    the \numSubjs{} projects we analyzed (\ie{}, nearly 1 in every 4
    projects) take at least 1 minute to run and
    \percentLongRunning{} of them take at least 5 minutes to run.\Comment{
      (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{mdframed}

>>>>

It is important to note that we under-estimated running times as we missed test modules not enabled for
execution in the root \emph{pom.xml}.\Comment{Some projects may omit long-running tests on their default
execution.}  For instance, the project \CodeIn{springboot-security-jwt}
runs all unit tests in a few seconds.  According to our criteria, this
project is classified as \shortg{} but a closer look reveals
that only smoke tests are executed in this project by default.
In this project, integration and system tests, which take longer to run, are only accessible via
custom parameters, which we do not handle in our experimental setup.
We enabled such parameters for this specific project and observed that
testing time goes to nearly 30 minutes.  For simplicity, we considered
only the tests executed by default.
From the \numSubjs{} testable projects, \numSubjsPass{} successfully
executed all tests and \numSubjsFail{} reported some test failure.
From these \numSubjsFail{} subjects, only 9 subjects
have more than 5\% of failing tests (5.1\% on average).
\begin{mdframed}
\noindent\textit{Answering \numRQFeasibilityOne{}:}~\emph{We conclude that
    time-consuming test suites are relatively frequent in
    open-source projects.  We found that \percentMedRunning{} of
    the \numSubjs{} projects we analyzed (\ie{}, nearly 1 in every 4
    projects) take at least 1 minute to run and
    \percentLongRunning{} of them take at least 5 minutes to run.\Comment{
      (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{mdframed}
